---
title: "individual1"
author: "Colin Willenborg"
date: "9/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
```

```{r}

choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
# Rating Distribution
hist(choco$Rating, breaks = 10, xlab="Rating", main="Histogram of Chocolate Ratings")

```

```{r}
boxplot(choco$Rating)
```

From this histogram we can see that the majority of the ratings fall in the 3-3.5 range. The boxplot shows there are outliers around 2.0 and lower for the rating and although the max rating is 5 there are no ratings above a 4 so that is one piece of information I found interesting.

```{r}
#Problem 2:
chocoYearRating <- choco[,c('Date', 'Rating')]
chocoYearRating <- chocoYearRating %>%
  arrange(chocoYearRating$Date)
aggregate(Rating ~ Date, data = chocoYearRating, mean)
Table2 <- addmargins(table(chocoYearRating), 2)
chocoSum <- as.data.frame(Table2)
chocoSum <- chocoSum[chocoSum$Rating == "Sum", c('Date', 'Freq')]
barplot(chocoSum$Freq, names.arg = chocoSum$Date, xlab = "Year", ylab="Count of Ratings", main="# Ratings per Year")
```

```{r}
# Problem 3:
chocoCocoa <- aggregate(Cocoa_Percent ~ Rating, data =choco, mean)
plot(chocoCocoa, main="Cocoa Percent vs Average Rating")
```

```{r}
chocoYearRating <- choco[,c('Cocoa_Percent', 'Rating')]
Table2 <- addmargins(table(chocoYearRating), 2)
chocoSum <- as.data.frame(Table2)
chocoSum <- chocoSum[chocoSum$Rating == "Sum", c('Cocoa_Percent', 'Freq')]
chocoSum <- chocoSum %>%
  arrange(Freq) %>%
  tail(5)
chocoSum
```
The table shows that the highest rated percentages are 70, 75, and 72 which means the majority of the chocolate bars made have a percentage of 70, 75, and 72.

```{r}
choco
chocoCocoa <- aggregate(Rating ~ Characteristics1, data =choco, mean, na.action = na.omit)
chocoCocoa2 <- aggregate(Rating ~ Characteristics2, data =choco, mean, na.action = na.omit)
chocoCocoa3 <- aggregate(Rating ~ Characteristics3, data =choco, mean, na.action = na.omit)
chocoCocoa4 <- aggregate(Rating ~ Characteristics4, data =choco, mean, na.action = na.omit)
chocoCocoa %>%
  rename(
    Characteristics = Characteristics1
  )
chocoCocoa2 %>%
  rename(
    Characteristics = Characteristics2
  )
chocoCocoa3 %>%
  rename(
    Characteristics = Characteristics3
  )
chocoCocoa4 %>%
  rename(
    Characteristics = Characteristics4
  )
chocoCocoa
rbind(chocoCocoa, chocoCocoa2, chocoCocoa3, chocoCocoa4)
```
